---
title: "MoonNMR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MoonNMR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}


```

---

#### Local Server Version

MoonNMR local version provides a similar experience as the online version hosted on shinyapps.io. In addition, the local version
This local version uses a single function to call -\> run_moonnmr(). Dependencies are automatically installed.
Before running MoonNMR the first time, it is recommended to run the function
```
moonnmr_archivecreator()
```
This creates the necessary archive files. Afterwards the table can also be populated with previous samples.


Simply run:
```
    library(MoonNMR)
    run_moonnmr()
```
---

For detailed information visit:
https://github.com/funkam/MoonNMR

For the web version visit: <https://funkam.shinyapps.io/MoonShiny/>

---
